---
title: "Lab 11 - Smoking during pregnancy"
author: "Lindsay Stall"
date: "4/3/23"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
library(skimr)
library(infer)
```

```{r}
library(usethis)
use_git_config(user.name = "Lindsay Stall", 
               user.email = "stallm21@wfu.edu")
```



### Exercise 1

```{r}
data(ncbirths)
```

```{r}
summary(ncbirths)
```
The cases are babies, and there are 1000 cases.

### Exercise 2

```{r}
ncbirths_white <- ncbirths %>%
  filter(whitemom == "white")
```

```{r}
mean(ncbirths_white$weight)

```
The mean white of babies born to white mother is 7.25

### Exercise 3

Yes? I believe so.

```{r}
boot_df_weight <- ncbirths_white %>%
  specify(response = weight) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")

boot_df_weight <- boot_df_weight %>% 
  mutate(stat = (stat + (7.43-mean(ncbirths_white$weight))))

boot_df_weight %>% 
  ggplot(aes(x = stat)) +
  geom_histogram(color = "black",fill = "magenta", alpha = 0.5) +
  xlab("weight")

sum((boot_df_weight$stat <= (mean(ncbirths_white$weight))) / length(boot_df_weight$stat)) +
sum((boot_df_weight$stat >= (7.43+(7.43-mean(ncbirths_white$weight)))) / length(boot_df_weight$stat))
```


### Exercise 4
For a two-tailed test we would get a p-value of 0.002, which means there has been a significant change.


### Exercise 5

```{r}

ncbirths<-ncbirths %>% drop_na(habit)
```


```{r}
ggplot(ncbirths, aes(habit, weight, fill=habit)) +
  geom_bar(stat="summary") +
  xlab("Smoking Habit") + ylab("Baby Weight (lbs)") +
  scale_fill_brewer(palette = "Accent") +
  ggtitle("Birth Weights of Infants by Mother's Smoking Habit")
  theme(legend.position="none")
```

Smoker's babies weigh less


### Exercise 7

The null hypothesis would be that there is no difference in weight for babies with mothers that do or do not smoke.

```{r}
ncbirths_habit<- ncbirths %>%
  subset(select=c(weight, habit))
```

### Exercise 8 
Yes, I believe so (though honestly could use clarification)

```{r}
boot_df_smoker <- ncbirths_habit %>% 
  filter(habit == "smoker") %>%
  specify(response = weight) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")


boot_df_nonsmoker <- ncbirths_habit %>% 
  filter(habit == "nonsmoker") %>%
  specify(response = weight) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")

boot_df_diff <- (boot_df_nonsmoker$stat-boot_df_smoker$stat) %>% 
  as.data.frame() %>% 
  setNames("MeanDiff")

boot_df_diff_c <- (boot_df_diff$MeanDiff - mean(boot_df_diff$MeanDiff)) %>% 
  as.data.frame() %>% 
  setNames("MeanDiff")

sum((boot_df_diff_c$MeanDiff >= mean(boot_df_diff$MeanDiff))/length(boot_df_diff_c$MeanDiff)) +
sum((boot_df_diff_c$MeanDiff <= (mean(boot_df_diff$MeanDiff)*-1))/length(boot_df_diff_c$MeanDiff))
```

The p-value is 0.01, so there is a difference in birth weight of babies whose mothers smokes versus don't smoke.

### Exercise 10








